Decoding the Amplitude-Modulated Part the DCF77 Longwave Time Signal by using the Goertzel Algorithm

### 2024-08-22 paper/main.tex
Re-formatted hyperlinks in references.

\usepackage{cuted}
\usepackage{stfloats}
\usepackage{tabularray}
\usepackage{matlab-prettifier}

@@

\begin{thebibliography}{00}
\bibitem{b1} -, ``DCF77,'' 2024, Wikipedia entry. [Online]. Available: https://de.wikipedia.org/wiki/DCF77
\bibitem{b2} D. Priester and P. Hetzel and A. Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77,'' PTB Mitteilungen, 2004, [Online]. Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/4.42/dcf77.pdf
\bibitem{b3} D. Priester and P. Hetzel and A. Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77: 1959-2009 und darüber hinaus,'' PTB Mitteilungen, 2009, [Online]. Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/pdf/2009\_Bauch\_PTBM\_\_DCF77.pdf
\bibitem{b4} P. Hetzel, ``Time dissemination via the LF transmitter DCF77 using a pseudo-random phase-shift keying of the carrier,'' PTB Braunschweig, 1988, [Online]. Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/pdf/5\_1988\_Hetzel\_-\_Proc\_EFTF\_88.pdf
\bibitem{b5} -, ``DCF77 webpage,'' 2024, Official page of the PTB [Online]. Available: https://www.ptb.de/cms/en/ptb/fachabteilungen/abt4/fb-44/ag-442/dissemination-of-legal-time/dcf77.html
\bibitem{b6} R. G. Lyons, ``Understanding Digital Signal Processing,'' Third Edition, Prentice Hall, 2010.
\bibitem{b9} J. Hoffmann, ``Sampling bandpass signals,'' 2021, Internet Article. [Online]. Available: https://www.dsprelated.com/showarticle/1407.php
\bibitem{b10} F. Zaplata and M. Kasal, ``SDR Implementation for DCF77,'', 2013, IEEE Paper. [Online]. Available: https://ieeexplore.ieee.org/document/6530943
\bibitem{b7} -, ``Goertzel algorithm,'' 2024, Wikipedia entry. [Online]. Available: https://en.wikipedia.org/wiki/Goertzel\_algorithm
\bibitem{b8} K. Banks, ``The Goertzel Algorithm,'' 2002, Internet Article. [Online]. Available: https://courses.cs.washington.edu/courses/cse466/12au/calendar/Goertzel-EETimes.pdf
\bibitem{b11} R. G. Lyons, ``Setting the 3-dB Cutoff Frequency of an Exponential Averager,'' 2012, Internet Article. [Online]. Available: https://www.dsprelated.com/showarticle/182.php
\end{thebibliography}
\end{document}

>>>>

\usepackage{cuted}
\usepackage{stfloats}
\usepackage{tabularray}
\usepackage[hyphens]{url}
\usepackage{matlab-prettifier}

@@

\Urlmuskip=0mu plus 1mu
\begin{thebibliography}{00}
\bibitem{b1} -, ``DCF77,'' 2024, Wikipedia entry. [Online]. Available: \url{https://de.wikipedia.org/wiki/DCF77}
\bibitem{b2} D. Priester and P. Hetzel and A. Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77,'' PTB Mitteilungen, 2004, [Online]. Available: \url{https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung_4/4.4_zeit_und_frequenz/4.42/dcf77.pdf}
\bibitem{b3} D. Priester and P. Hetzel and A. Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77: 1959-2009 und darüber hinaus,'' PTB Mitteilungen, 2009, [Online]. Available: \url{https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung_4/4.4_zeit_und_frequenz/pdf/2009_Bauch_PTBM__DCF77.pdf}
\bibitem{b4} P. Hetzel, ``Time dissemination via the LF transmitter DCF77 using a pseudo-random phase-shift keying of the carrier,'' PTB Braunschweig, 1988, [Online]. Available: \url{https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung_4/4.4_zeit_und_frequenz/pdf/5_1988_Hetzel_-_Proc_EFTF_88.pdf}
\bibitem{b5} -, ``DCF77 webpage,'' 2024, Official page of the PTB [Online]. Available: \url{https://www.ptb.de/cms/en/ptb/fachabteilungen/abt4/fb-44/ag-442/dissemination-of-legal-time/dcf77.html}
\bibitem{b6} R. G. Lyons, ``Understanding Digital Signal Processing,'' Third Edition, Prentice Hall, 2010.
\bibitem{b9} J. Hoffmann, ``Sampling bandpass signals,'' 2021, Internet Article. [Online]. Available: \url{https://www.dsprelated.com/showarticle/1407.php}
\bibitem{b10} F. Zaplata and M. Kasal, ``SDR Implementation for DCF77,'', 2013, IEEE Paper. [Online]. Available: \url{https://ieeexplore.ieee.org/document/6530943}
\bibitem{b7} -, ``Goertzel algorithm,'' 2024, Wikipedia entry. [Online]. Available: \url{https://en.wikipedia.org/wiki/Goertzel_algorithm}
\bibitem{b8} K. Banks, ``The Goertzel Algorithm,'' 2002, Internet Article. [Online]. Available: \url{https://courses.cs.washington.edu/courses/cse466/12au/calendar/Goertzel-EETimes.pdf}
\bibitem{b11} R. G. Lyons, ``Setting the 3-dB Cutoff Frequency of an Exponential Averager,'' 2012, Internet Article. [Online]. Available: \url{https://www.dsprelated.com/showarticle/182.php}
\end{thebibliography}
\end{document}
